### 2023-04-10 main/chapter_theory.tex
c1n2 waffle more

\subsection{Specific simplified models}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ `$\twoljets$'
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.
\TODO{add citations}

\paragraph{C1N2.}
`C1N2' is a restricted subset of the MSSM in which the only active SUSY
particles
are the lightest chargino ($\chargino_1$)
and the lightest two neutralinos ($\neutralino_1$, $\neutralino_2$).
The name `C1N2` is an abbreviation to
`Chargino 1' concatenated with `Neutralino 2'.

>>>>

\subsection{Specific simplified models}
\TODO{add citations}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ `$\twoljets$'
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.
Many \atlas\ searches distribute their efforts across many simplified models.
This search patches just one part in the larger \atlas\ SUSY programme.

\paragraph{C1N2.}
`C1N2' is a restricted subset of the MSSM in which the only active SUSY
particles
are the lightest chargino ($\chargino_1$)
and the lightest two neutralinos ($\neutralino_1$, $\neutralino_2$).
The name `C1N2` is an abbreviation to
`Chargino 1' concatenated with `Neutralino 2'.
This model is active in the electroweak sector of the MSSM, which has received
increased interest in recent years because the LHC is more sensitive to models
in the strong sector.
Existing LHC have have already ruled out many strongly-interacting models
up to multi-$\eV[T]$ mass scales, but some viable phase space remains in the
electroweak sector.

Chargino-neutralino pairs could be produced in proton collisions via off-shell
$W$ boson propagators.
The targeted experimental signature is achieved by decays of these gauginos
to the $\neutralino_1$ LSP via emission of Standard Model particles.
